---
title: |
  | Models of Marine Protected Areas that
  | Omit Distance are Not Credible
author: 
  - Daniel Ovando
  - Owen Liu
  - Renato Molina
  - Cody Szuwalski
date: "`r Sys.Date()`"
output: bookdown::pdf_document2
linkcolor: blue
toc: false
bibliography: references.bib
csl: pnas.csl
params:
  results_name: ["v0.5"]
---

```{r setup, include=FALSE}
# run cabral-et-al-exploration.Rmd prior to knitting reply
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(sf)
library(here)
library(readr)
library(ggplot2)
library(patchwork)

theme_set(theme_classic())

results_name <- params$results_name

results_path <- here("results", results_name)

if (!dir.exists(results_path)){
  dir.create(results_path, recursive = TRUE)
}

upsides_summary <- read_rds(file = file.path(results_path,"upsides_summary.rds"))

reply_plot <- read_rds(file = file.path(results_path,"reply_plot.rds"))


```

<!-- an error in their business-as-usual (BAU) policy produces meaningfully different results if corrected, reducing the projected food benefits from MPAs by roughly 30%, as well as altering their global MPA prioritization map. Beyond this error though, -->

We agree with three broad points raised by Cabral *et al.* 2020 [@cabral2020]: 1) Marine Protected Areas (MPAs) can play an important role in conservation and food security, 2) much of the high seas could be closed to fishing without substantially reducing global catch and 3) much of the food-security benefits of MPAs could be achieved by targeted protection in a few key places. However, beyond an error in their original  business-as-usual policy that alters their results meaningfully, their model makes a series of questionable assumptions that produce results inconsistent with best available knowledge of the state of global fisheries and fish ecology.

Cabral *et al.*'s model assumes that all unassessed stocks of the same species comprise a single perfectly interconnected population, based on probability of occurrence estimates from Aquamaps [@kaschner2019]. This results in the median geographic range of an unassessed stock according to their model being 17 times that of an assessed stock, which is not credible and distorts the optimal size of MPA networks. Ignoring the distance between patches of ocean, and assuming that fishing mortality is equal everywhere, results in illogical results like MPAs placed in Australia providing equal benefits to areas as far apart as Indonesia and Mexico (Fig.\@ref(fig:reply-fig)a), and closures off of the Americas benefiting species only caught near China (Fig.\@ref(fig:reply-fig)b).

The global MPA network for food production resulting from this distance-free model should give MPA stakeholders of all kinds pause. Using the corrected BAU policy for RAM stocks, Cabral *et al.*'s food maximizing MPA network would close 22% of the USA's EEZ to fishing, yet places only 2.5% of India's, 10% of Indonesia's, and 12% of China's EEZ in MPAs (Fig.\@ref(fig:reply-fig)b). Costello *et al.*. 2016 [@costello2016] estimated that the median $F/F_{MSY}$ (fishing mortality rate *F* relative to the fishing mortality rate producing maximum sustainable yield *F~MSY~*) of fisheries in India, Indonesia, and China is nearly twice that of the USA, creating almost five times as much potential food upside from fishery reforms in those regions relative to the USA. Based solely on the results presented in the paper users have no way of knowing whether the purported food benefits of MPAs in an area highlighted by Cabral *et al.* stem from these sorts of trans-oceanic connections.

Any global model must make simplifying assumptions, but the assumptions made in Cabral *et al.* 2020 are not necessary and lead to misleading results. A global model of MPAs must consider biological constraints of movement and spatial heterogeneity of fishery institutions. Reducing the effective range of populations by following the same stock structure as Costello *et al.* (2016) would be a start in this direction, but explicitly modeling the role that distance plays in ecological and economic responses to MPAs would be preferred. Either of these approaches would be computationally intensive but feasible, and we suspect would produce markedly different results from the findings they currently report.

```{r reply-fig, fig.cap = "Assumptions of Cabral *et al.* 2020 produce results that are not credible.  Panel *a* shows the distribution of food increases, omitting tunas, generated by a network of MPAs covering Australia's EEZ according to the Cabral *et al.* 2020 model, with MPAs shown in red, and color of individual non-MPA cells showing the predicted food benefits generated by the Australian MPAs in that cell, scaled by the maximum food benefits generated by these MPAs in any cell. White areas show cells with benefits divided by maximum benefits less than 0.01. Panel *b* shows percent of each country's exclusive economic zone (EEZ) protected under Cabral *et al.* 2020's food maximizing MPA network under their business as usual (BAU) policy, applying the BAU correction for RAM stocks. Text percentages show percent of MPA-generated food benefits for overfished unassessed species caught nearly exclusively in the Pacific Northwest FAO region originating from FAO regions outside the Pacific Northwest according to Cabral *et al.* 2020. White areas are outside of EEZs."}
reply_plot
```

\newpage

# References
